---
title: "Wild Data Mack Creek"
author: "Julia Parish"
date: "8/10/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(here)
library(janitor)

```
## Read in the data using read_csv() with here(), store as mack_verts

```{r}
mack_verts <- read_csv(here::here("data", "AS00601.csv"))
mack_verts

# Update the names to lower_snake_case

mack_verts <- mack_verts %>% clean_names()

```

# # In a new code chunk, practice accessing individual pieces of the data frame (there is no real functionality to this, but just to reinforce stuff we learned in our interactive session):
- Store the 5th value in column “WEIGHT” as mc_wt_5. Check by looking at your data frame to confirm.
- Store the 8th - 20th value in the “LENGTH1” column as mc_length_8_20. Check by looking at your data frame to confirm.
- Store everything in column SAMPLEDATE as a vector called mc_dates

```{r}
mc_wt_5 <- mack_verts$weight[5] 
mc_wt_5

mc_length_8_20 <- mack_verts$length1[8:10]
mc_length_8_20

mc_dates <- mack_verts$sampledate
mc_dates

```
## Make a salamander subset - create a subset that only contains observations for Pacific Giant Salamanders (species Dicamptodon tenebrosus, stored in species as DITE). Store the subset as mc_salamanders. Hint: see dplyr::filter()

```{r}
mc_salamanders <- mack_verts %>% 
  filter(species== "DITE")

```

# Make a scatterplot
 - Create a scatterplot of length1 (snout-vent length in millimeters) versus weight (grams) for all salamanders in the dataset. 
*If you have a variable you see as "explanatory" and the other one as the thing being explained, then one (very common) convention is to put the explanatory variable on the x-axis and the thing being explained by it on the y-axis. In some cases, if one variable is 'fixed' and the other is 'random', the more common convention is that random one tends to go on the y-axis of the plot.*
 - Update axis labels, title, subtitle, and add a caption with the data source. Customize point color and size, possibly opacity, and theme.
  - **x and y** : the x and y co-ordinates to be used to position the legend; 
  - **legend** : the text of the legend; 
 - **fill** : colors to use for filling the boxes beside the legend text; 
 - **col** : colors of lines and points beside the legend text
 - **bg** : the background color for the legend box.
 - Export your scatterplot as salamander_size.png to your figs folder.

```{r}
mc_salamanders_plot <- 
  ggplot(data = mc_salamanders, 
         aes(x = length1, y = weight)) + 
  geom_point(aes(size = length1, color = weight), 
             # color = "green",
             alpha = 0.25, 
             show.legend = TRUE) +
  scale_size_continuous(breaks = c(50, 100, 150), 
                        labels = c("50mm", "100mm", "150mm"),
                        guide = "none") +
  labs(title = "Mack Creek Salamanders", 
       x = "Snout to Vent Length (mm)", 
       y = "Weight (g)",
       size = "Salamander Length") +
  theme_classic() + 
  theme(legend.position = "bottom")

mc_salamanders_plot

ggsave(here::here("figs", "salamander_size.png"),
       height = 6, width = 6)

```
# **Make a cutthroat plot**
- Similar to above, make a subset called mc_trout that only contains observations for cutthroat trout
- Create a scatterplot of length1 by weight for all trout in the dataset
- Customize so that the point color depends on reach
- Customize your color scheme (e.g. scale_color_manual())
- Facet your plot by creek reach (facet_wrap(~...))
- Update graph axis labels and title
- Export your graph as cutthroat_size.png to figs

- to change the strip (L,M,U) your facet wrap is attached to this reach column, need to add a new column with if else test
 then facet wrap by new column 

```{r}
reach_labels <- c(L = "Lower", M = "Middle", U = "Upper")
mc_trout <- mack_verts %>% 
  filter(species== "ONCL") %>% 
  mutate(reach_label = reach_labels[reach])

mc_cutthroat_plot <- 
  ggplot(data = mc_trout,
    aes(x = length1, y = weight)) + 
  geom_point(aes(color = reach),
    show.legend = FALSE) + 
  scale_color_manual(values = 
                       c("L" = "dark blue", 
                         "M" = "forest green",
                         "U" = "salmon")) +
  labs(title = "Cutthroat Trout Reach",
       x = "Trout Length (mm)", 
       y = "Weight (g)") +
  facet_wrap(~reach_label)
  
mc_cutthroat_plot
  
```

