---
title: "Wild Data Mack Creek"
author: "Julia Parish"
date: "8/10/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(here)
library(janitor)

```
## Read in the data using read_csv() with here(), store as mack_verts

```{r}
mack_verts <- read_csv(here::here("data", "AS00601.csv"))
mack_verts

# Update the names to lower_snake_case

mack_verts <- mack_verts %>% clean_names()

```

# # In a new code chunk, practice accessing individual pieces of the data frame (there is no real functionality to this, but just to reinforce stuff we learned in our interactive session):
- Store the 5th value in column “WEIGHT” as mc_wt_5. Check by looking at your data frame to confirm.
- Store the 8th - 20th value in the “LENGTH1” column as mc_length_8_20. Check by looking at your data frame to confirm.
- Store everything in column SAMPLEDATE as a vector called mc_dates

```{r}
mc_wt_5 <- mack_verts$weight[5] 
mc_wt_5

mc_length_8_20 <- mack_verts$length1[8:10]
mc_length_8_20

mc_dates <- mack_verts$sampledate
mc_dates

```
## Make a salamander subset - create a subset that only contains observations for Pacific Giant Salamanders (species Dicamptodon tenebrosus, stored in species as DITE). Store the subset as mc_salamanders. Hint: see dplyr::filter()

```{r}
mc_salamanders <- mack_verts %>% 
  filter(species== "DITE")

```

