---
title: "r_data_types"
author: "Julia Parish"
date: "8/10/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 1. Create a vector called vec_1containing the following:
2, 5, 9, 10, 8, 12, 1, 0
Check the following for that vector:
- What is the class of the vector? class()
- What type of variable does it store? typeof()
- Access the 3rd element and store as vec_1_e3
- Access the 1st element and store as vec_1_e1
- Access the 5th through 7th elements and store as vec_1_e5to7
- Reassign vec_1 as a character using as.character, stored as vec_1_char. What does the output look like?
```{r}
vec_1 <- c(2, 5, 9, 10, 8, 12, 1, 0)
vec_1

class(vec_1)
# numeric

# What type of variable does it store
typeof(vec_1)
# double

# Access the 3rd element and store as vec_1_e3

vec_1_e3 <- vec_1[3]
vec_1_e3

# Access the 1st element and store as vec_1_e1

vec_1_e1 <- vec_1[1]
vec_1_e1

# Access the 5th through 7th elements and store as vec_1_e5to7

vec_1_e5to7 <- vec_1[5:7]
vec_1_e5to7

# Reassign vec_1 as a character using as.character, stored as vec_1_char. What does the output look like?

vec_1_char <- as.character(vec_1)
vec_1_char

```
## Create a vector called vec_2
vec_2 should contained named elements, where town = "Santa Barbara, location = "Rincon", swell = "south"

```{r}
vec_2 <- c(town = "Santa Barbara", location = "Rincon", swell = "south")

vec_2

class(vec_2)

typeof(vec_2)

vec_2[2]

vec_2["location"]

# What is the class of vector elements? class() - character
# What is the length of vec_2? - 3
# Access the 2nd element by name and store as vec_2_e2

vec_2_e2 <- vec_2["location"]
vec_2_e2

```

## Create a data frame in R, index
## Write code to create a data frame called df_1 that looks like this:
- ##   region     species count
- ## 1      A       otter    12
- ## 2      B great white     2
- ## 3      A    sea lion    36
- ## 4      D  gray whale     6

```{r}
df_1 <- data.frame(region = c("A", "B", "A","D"),
                   species = c("otter", "great white", "sea lion", "gray whale"),
                   count = c(12, 2, 36, 6))
df_1  

class(df_1)
# data.frame

# Return the class of the species column
class(df_1$species)
# character

# Find the maximum value of the count() column, store as max_count

max_count <- max(df_1$count)
max_count

# More functions - min, mean, etc..
# Shortcuts - shift + (, shift + `, shift + " will wrap the text in these symbols  

```

